% (c)  2020 Jumar Martin <jumar@jumart.in> https://jumart.in

%This work is licensed under the Creative Commons Attribution 4.0 International License. To view a copy of this license, visit https://creativecommons.org/licenses/by/4.0/

\documentclass{sga-bill}

\author{Jumar Martin}
\sponsor{}
\second{}

\speaker{Louisa Sholar}
\secretary{Julia Field}
\president{Jack Johnson}

\aye{}
\nay{}
\abstain{}
\status{PASSED}

\date{\today}

\billtitle{Allocate Reserve Funds To Support Student and Iconic Art and Outdoor Spaces Equipment on Campus}

\billcode{20-2.4}

\begin{document}
\maketitle

\whereas{The Elon University Student Government Association seeks to promote school spirit and initiatives that improve life on campus}

\whereas{There is a need to provide better support to student art initiatives and provide more infrastructure related to the enjoyment of outdoor spaces on campus}

\whereas{The Elon University Student Government Association has the opportunity to allocate reserve fund savings to spend towards area of student interest and benefit to the community}

\whereas{Such an undertaking must also require the collaboration of several individuals on campus}

\therefore

\article{1}{The Elon University Student Government Association shall convene two advisory and oversight committees on
\textit{student and iconic art and outdoor spaces equipment, respectively.} The two committees will be responsible for employing a total of \$330,000.00 towards their designated areas.
    \begin{sub}
        \item 
            The Student and Iconic Art Committee will receive \$30,000.00 in funding.
        \item 
            The Outdoor Spaces Equipment Committee will receive \$300,000.00 in funding.
    \end{sub}
}

\article{2}{The committees shall be responsible for all planning, budgeting, purchasing, and executing of given projects over a two-year period ending on May 31st, 2022. The committees shall be autonomous, coalition groups comprised of university staff, faculty, and students.
    \begin{sub}
        \item 
            during meetings and shall organize the voting process. A simple majority of the committee shall be required to approve a purchase. The co-chairs shall consist of one faculty/staff person and one student.
        
        \item 
            Students serving on the committees shall be voting members, and they shall be required to share updates with the Student Government Association.
    \end{sub}
}

\article{3}{The Student and Iconic Art Committee will ensure that all funded projects have a goal of increasing school spirit and/or allow for more student expression on campus in line with Elon's aesthetic values; including, but not limited to: decorative structures, “living” art, indoor student art pieces for common university spaces, etc.}

\article{4}{The Outdoor Spaces Equipment Committee will ensure that all funded projects have a goal of improving campus’s outdoor spaces; \out{including, but not limited to:}\add{for example:} the purchase of fire pits, tables, benches, chairs, outdoor gyms, etc.}

\article{5}{The committees will be coordinated by the Executive President and will include members of university administration, faculty, and students.
    \begin{sub}
        \item 
            The Student and Iconic Art Committee shall consider the following as voting members or advisors: the director of Physical Plant (or a designated individual), the Director of Landscaping (or a designated individual), the university art curator, the university interior designer, a student representative from the Traditions Council, a representative of University Admissions, one member from the SGA Executive Board, and relevant student appointees associated with these departments.
        
        \item 
            The Outdoor Spaces Equipment Committee shall consider the following as members or advisors: the director of Physical Plant (or a designated individual), a representative from Resident Life, a represented from Campus Recreation and Wellness, a Faculty in Residence member, one member from the SGA Executive Board, and relevant student appointees associated with these departments.
    \end{sub}
}

\article{6}{It shall be the responsibility of the Executive President and Executive Vice President of the Student Government Association to help organize the committees and remain committed to ensuring the success of their respective responsibilities over the designated time period. The Executive President shall nominate students for the committees and each nomination must be approved by a majority of the Executive Board.}

\signatures
\end{document}
