%-------------------------
% Resume, a LaTeX resume template for developers
% Author: Christian Bueno
% Based on: https://github.com/christianbueno1/latex-pilot
% License: MIT
%-------------------------



%------------PACKAGES----------------
\documentclass[a4paper,11pt]{article}

% Design and typography packages
\usepackage{titlesec}     % custom section formatting
\usepackage{enumitem}     % control over lists (itemize, enumerate)
\usepackage{fancyhdr}     % header and footer customization
\usepackage[empty]{fullpage} % custom page margins
\usepackage{array}        % custom table column formatting

% Links and text formatting
\usepackage[hidelinks]{hyperref} % clickable links without borders
\usepackage[normalem]{ulem}      % underlining with line break support

% Color support (modern version)
\usepackage{xcolor}       % advanced color management

% Language support
\usepackage[english]{babel} % English typographic rules
%-----------------------------------------

\input glyphtounicode % converts glyph names to unicode
\pdfgentounicode=1 % ensures generated PDFs are ATS-readable

%----------FONT OPTIONS-------------------
\usepackage[default]{sourcesans} % use Source Sans font
\urlstyle{same} % URLs use the same font as the document
%-----------------------------------------


%----------MARGIN OPTIONS-----------------
\pagestyle{fancy} % customizable page style with fancyhdr
\fancyhf{} % clear all header and footer fields

\renewcommand{\headrulewidth}{0in} % header line thickness to zero
\renewcommand{\footrulewidth}{0in} % footer line thickness to zero

\setlength{\tabcolsep}{0in} % table column separator thickness to zero
\setlength{\footskip}{4.08003pt} % minimum footer space (avoids warnings)

% document origin is one inch from top and left
% oddsidemargin and evensidemargin refer to the left margin
% right margin is adjusted indirectly using oddsidemargin
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\topmargin}{-0.5in}

\addtolength{\textwidth}{1.0in} % increase text area width by one inch
\addtolength{\textheight}{1.0in} % increase text area height by one inch

\raggedbottom{} % all pages have the height of the current page, no extra vertical space
\raggedright{} % all pages have the width of the current page, no extra horizontal space
%------------------------------------------


%--------SECTION COMMANDS---------
% \titleformat{<command>}
%   [<shape>]{<format>}{<label>}{<sep>}
%     {<before-code>}[<after-code>]

% command: the section command to redefine (e.g., \section)
% shape: font style; scshape = small caps
% format: format applied to the complete title - label and text
% label: defines the section label
% sep: horizontal separation between label and title body
% before-code: code executed before the title
% after-code: code executed after the title

\titleformat{\section}
  {\scshape\large}{}
    {0em}{\color{blue}}[\color{black}\titlerule\vspace{0pt}]
%-------------------------------------


%--------REDEFINITIONS----------------
% redefine underline depth to 2pt
\renewcommand{\ULdepth}{2pt}
%-------------------------------------


%--------CUSTOM COMMANDS--------------
% \vspace{} defines a vertical space of given size, modifying it in custom commands 
% helps to stretch or shrink the CV to remove or add content

% resumeItem renders a bullet point
\newcommand{\resumeItem}[1]{
  \item\small{#1}
}

% commands to start and end resumeItem itemization
% rightmargin adjusted to 0.11in to avoid resumeItem overflow
\newcommand{\resumeItemListStart}{\begin{itemize}[rightmargin=0.11in]}
\newcommand{\resumeItemListEnd}{\end{itemize}}

% resumeQuadHeading renders four elements in two columns
% second row in italics and first element of first row in bold
% can be used for experience and projects with four elements
\newcommand{\resumeQuadHeading}[4]{
  \item
  \begin{tabular*}{0.96\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}
}

% commands to start and end resumeQuadHeading itemization
% leftmargin for 0.15in left indentation for resumeItems
\newcommand{\resumeHeadingListStart}{
  \begin{itemize}[leftmargin=0.15in, label={}]
}
\newcommand{\resumeHeadingListEnd}{\end{itemize}}

% commands for contact details
\newcommand{\name}[1]{\textbf{\Huge #1}}
\newcommand{\socialLinks}[1]{#1}
\newcommand{\separator}{$|$}
%-------------------------------------------


%__________________RESUME____________________
% You can reorganize sections in your preferred order
\begin{document}

%-----------CONTACT DETAILS------------------

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \name{Christian Bueno \vspace{2pt}} & 
  Location: Guayaquil, Guayas, Ecuador \\
  
  \socialLinks{
    \href{https://www.christianbueno.work}{\uline{christianbueno.work}} \separator{}
    \href{https://www.linkedin.com/in/christianbueno1/}{\uline{LinkedIn}} \separator{}
    \href{https://github.com/christianbueno1}{\uline{GitHub}} \separator{}
    \href{https://www.instagram.com/christianbueno.1/}{\uline{Instagram}}
  } & 
  Email: \href{mailto:chris@deployhero.dev}{\uline{chris@deployhero.dev}} \\
  
  & mobile: +593 99 028 8710 \\
\end{tabular*}
%--------------------------------------------


%--------------TECHNICAL SKILLS------------------------
\section{Technical Skills}
\begin{tabular}{@{}p{3.2cm}>{\raggedright\arraybackslash}p{12.8cm}@{}}
  \textbf{DevOps:} & Jenkins, Terraform/OpenTofu, Ansible, Kubernetes, Serverless Framework, Maven \\
  \textbf{Languages:} & Python 3.13, JavaScript, TypeScript, Java 25 \\
  \textbf{Backend:} & Spring Boot 4, Spring Security 7, Spring Data JPA, Hibernate, Jakarta Validation, Lombok \\
  \textbf{Cloud / IoT:} & AWS Lambda, API Gateway, EventBridge, DynamoDB, S3, event-driven architectures, IoT simulation \\
  \textbf{AI / LLM:} & LangChain, LangGraph, LangMem, OpenAI API (GPT-4o-mini), pgvector \\
  \textbf{Frameworks:} & NestJS, Express.js, FastAPI, Django, Flask, Tailwindcss, Next.js \\
  \textbf{Databases:} & PostgreSQL 18, pgvector, MySQL/MariaDB, SQL Server, MongoDB, Apache Cassandra \\
  \textbf{Security:} & Spring Security 7 (OTT passwordless), RBAC, SOPS + age (AES256-GCM) \\
  \textbf{Tools:} & Git, Vite, AWS, Linode, Docker, Podman, Linux, Node.js, uv \\
  \textbf{Design:} & Kdenlive, Inkscape, GIMP, Canva, ChatGPT, Midjourney, OpenAI API \\
\end{tabular}
%--------------------------------------------


%-----------EXPERIENCE-----------------------
% Distill all your key points into small bullets following the "challenge-action-result" pattern
% for maximum efficiency. Quantify (use numbers) your achievements when possible, highlight important words

\section{Experience}
\resumeHeadingListStart{}

  \resumeQuadHeading{AI / Backend Developer}{2025 -- 2026}
  {Multichannel Virtual Assistant LLM+RAG --- Personal Project}{Guayaquil, Guayas, Ecuador}
    \resumeItemListStart{}
      \resumeItem{Built a multichannel virtual assistant with \textbf{LangGraph} and \textbf{LangChain}, implementing agentic conversation flows with \textbf{GPT-4o-mini} and \textbf{13 tools} via function calling (properties, appointments, memory).}
      \resumeItem{Implemented \textbf{RAG} with \textbf{pgvector} and OpenAI Embeddings (\textit{text-embedding-3-small}, 1536 dims) for cosine similarity semantic search over a real estate inventory.}
      \resumeItem{Designed multi-namespace persistent semantic memory with \textbf{LangMem} and \textbf{PostgreSQL} (client profiles, properties, interactions), with conversational state checkpointing by \texttt{phone\_number}.}
      \resumeItem{Built async REST API with \textbf{FastAPI} + \textbf{Uvicorn} and integrated WhatsApp webhooks via \textbf{WAHA} (WhatsApp HTTP API) for real-time inbound message processing.}
      \resumeItem{Containerized \textbf{PostgreSQL + pgvector} with \textbf{Docker} and managed dependencies with \textbf{uv}, optimizing costs with token caching (\textbf{50\%} discount) and condensed prompts.}
    \resumeItemListEnd{}

  \resumeQuadHeading{Backend Developer}{2025 -- 2026}
  {StockPilot API --- Personal Project}{Guayaquil, Guayas, Ecuador}
    \resumeItemListStart{}
      \resumeItem{Developed RESTful inventory management API with \textbf{Spring Boot 4} and \textbf{Java 25}, implementing full CRUD with \textbf{Spring Data JPA} and \textbf{PostgreSQL 18}.}
      \resumeItem{Implemented passwordless authentication with \textbf{Spring Security 7} One-Time Token (OTT), eliminating credential leak risks via email-based login flow.}
      \resumeItem{Designed role-based access control (\textbf{RBAC}) with granular per-endpoint authorization (ROLE\_ADMIN, ROLE\_USER, public) using declarative \textbf{SecurityFilterChain}.}
      \resumeItem{Applied layered architecture (Controller $\rightarrow$ Service $\rightarrow$ Repository) with DTO pattern, \textbf{Jakarta Bean Validation} and centralized error handling with \textbf{@RestControllerAdvice}.}
      \resumeItem{Containerized \textbf{PostgreSQL} with rootless \textbf{Podman} and \textbf{Kubernetes} manifests, externalizing configuration with ConfigMaps and Secrets.}
      \resumeItem{Implemented secrets encryption at rest with \textbf{SOPS + age} (AES256-GCM) for secure credential management in Git.}
    \resumeItemListEnd{}

    \resumeQuadHeading{Full Stack Developer}{2025 -- 2026}
    {Clasify --- Personal Project}{Guayaquil, Guayas, Ecuador}
      \resumeItemListStart{}
        \resumeItem{Built a full-stack tutoring marketplace with \textbf{ASP.NET Core Web API} and \textbf{Blazor Server} (.NET 10), enabling teacher onboarding and verification, student bookings, and reviews.}
        \resumeItem{Applied \textbf{Clean Architecture} in 4 layers (Domain, Application, Infrastructure, API) and designed a \textbf{Person}-centric model with \textbf{[Flags]} roles (\textbf{Teacher}/\textbf{Student}) to prevent duplicate profiles.}
        \resumeItem{Implemented secure auth with \textbf{JWT Bearer} (15-min access tokens), 7-day rotating refresh tokens, Redis \textbf{jti} blocklist logout, and \textbf{PBKDF2} password hashing.}
        \resumeItem{Implemented admin teacher verification and tiered \textbf{Free / Starter / Pro} subscriptions to control access to teacher features.}
        \resumeItem{Developed REST resources (Auth, Teachers, Students, Subjects, Bookings, Reviews, Availability, and Subscriptions) with soft delete, pagination, and filtering.}
        \resumeItem{Set up reproducible local infrastructure with \textbf{Podman} (\textbf{PostgreSQL 18 + pgvector} and \textbf{Redis} in isolated pods/network with persistent volumes) using a single setup script.}
      \resumeItemListEnd{}

\resumeQuadHeading{Cloud / Backend Developer}{2024 -- 2025}
  {IoT Pulse --- Serverless IoT monitoring simulator on AWS}{Guayaquil, Guayas, Ecuador}
  \resumeItemListStart{}
    \resumeItem{Developed an end-to-end IoT monitoring platform on \textbf{AWS} using \textbf{Serverless Framework}, showcasing event-driven architecture and cloud-native patterns for use cases in manufacturing, agriculture, and logistics.}
    \resumeItem{Designed and implemented a real-time data pipeline with \textbf{AWS EventBridge} (cron scheduling) $\rightarrow$ \textbf{AWS Lambda} (Python) $\rightarrow$ \textbf{DynamoDB}, simulating \textbf{5 industrial sensors} with realistic data generation and threshold-based alert detection.}
    \resumeItem{Built a REST API with \textbf{API Gateway} exposing endpoints for historical data, real-time readings, and device alerts.}
    \resumeItem{Implemented an automated seed process to populate \textbf{7 days} of history, enabling trend analysis from the first deploy.}
    \resumeItem{Deployed a static dashboard on \textbf{S3} to visualize sensor metrics and time-series evolution.}
    \resumeItem{Stack: \textbf{Python}, \textbf{AWS Lambda}, \textbf{API Gateway}, \textbf{DynamoDB}, \textbf{EventBridge}, \textbf{Serverless Framework}, \textbf{S3}.}
\resumeItemListEnd{}

\resumeQuadHeading{Data Analyst}{Aug 2024 -- Sep 2024}
  {\href{https://www.guayaquil.gob.ec/}{\uline{Nostrum}}}{Guayaquil, Guayas, Ecuador}
  \resumeItemListStart{}
    \resumeItem{Automated address matching with \textbf{Python} and \textbf{CustomTkinter}, reducing processing time by \textbf{75\%}.}
    \resumeItem{Processed multiple Excel files with efficient algorithm using \textbf{Pandas} and configurable similarity thresholds.}
    \resumeItem{Implemented modular architecture separating UI, business logic and data processing to improve maintainability.}
    \resumeItem{Integrated real-time progress tracking for datasets with thousands of records.}
\resumeItemListEnd{}

\resumeQuadHeading{Web Development}{Jul 2023 -- Jan 2024}
  {\href{https://contabilly.com}{\uline{Contabilly S.A.S.}}}{Guayaquil, Guayas, Ecuador}
    \resumeItemListStart{}
      \resumeItem{Developed sales management system with appointment scheduling and contact management.}
      \resumeItem{Built frontend with \textbf{React}, \textbf{Redux Toolkit}, validation with \textbf{Formik/Yup} and \textbf{Material UI}.}
      \resumeItem{Implemented backend with \textbf{Express.js}, \textbf{MySQL} and \textbf{Sequelize} as ORM.}
    \resumeItemListEnd{}

  \resumeQuadHeading{Web Development}{Oct 2022 -- Dec 2022}
  {\href{https://high-track.com/}{\uline{High-Track}}}{Guayaquil, Guayas, Ecuador}
    \resumeItemListStart{}
      \resumeItem{Implemented validation system for managing students, buses, drivers and school routes.}
      \resumeItem{Developed GPS-NMEA tracking module using \textbf{RMC/\$GPRMC} standard for real-time vehicle tracking.}
      \resumeItem{Worked with \textbf{Django}, \textbf{Bootstrap}, \textbf{jQuery} improving user experience by \textbf{10\%}.}
    \resumeItemListEnd{}

  \resumeQuadHeading{Full Stack Developer}{Jan 2018 -- 2024}
  {\href{https://christianbueno.work}{\uline{www.christianbueno.work}}}{Guayaquil, Guayas, Ecuador}
    \resumeItemListStart{}
      \resumeItem{Developed and deployed \textbf{7 projects} (e-commerce, corporate, SaaS tools) using \textbf{React}, \textbf{TypeScript}, \textbf{FastAPI}, \textbf{WordPress} and \textbf{Tailwind CSS}.}
      \resumeItem{Automated deployments with \textbf{Podman}, \textbf{Shell scripts}, building images, pods, containers and volumes for data persistence.}
      \resumeItem{Managed infrastructure as code with \textbf{OpenTofu} (DigitalOcean, Azure, AWS) and \textbf{Ansible} for VM provisioning, firewall configuration and web servers on \textbf{RedHat/Rocky/Ubuntu Linux}.}
      \resumeItem{Managed DNS with \textbf{Cloudflare} and delivered complete projects including e-commerce, landing pages, mobile apps and corporate systems.}
    \resumeItemListEnd{}
    
\resumeHeadingListEnd{}
%---------------------------------------------




%-----------SUMMARY--------------------------
% Keep this short, simple and to the point

\section{Biography}
\small{
  \textbf{Full Stack, Backend, AI Developer and DevOps Specialist} with over 6 years of experience building and deploying technology solutions. Computer Science Engineering student at ESPOL (graduating soon). I specialize in RESTful API development, conversational AI systems and infrastructure automation. I build APIs with \textbf{Java 25} and \textbf{Spring Boot 4} applying modern security (OTT passwordless authentication, \textbf{RBAC}, encryption with \textbf{SOPS + age}), and AI systems with \textbf{LangGraph}, \textbf{LangChain} and \textbf{RAG} over \textbf{pgvector}. I also design cloud-native serverless solutions on \textbf{AWS} for real-time IoT monitoring, integrating \textbf{EventBridge}, \textbf{Lambda}, \textbf{DynamoDB}, \textbf{API Gateway}, and \textbf{S3}-based dashboards. In DevOps, I use \textbf{Podman}, \textbf{OpenTofu}, \textbf{Ansible} and \textbf{CI/CD} to scale projects reliably. I have deployed 7+ projects in production including e-commerce, SaaS and corporate systems. Looking for opportunities to work on challenging projects combining backend development, AI, cloud, and modern DevOps practices.
}
%--------------------------------------------


%-----------EDUCATION-------------------------
% Mention your GPA if it's good, in the first row of the second column

\section{Education}
  \resumeHeadingListStart{}
    \resumeQuadHeading{Escuela Superior Politécnica del Litoral - ESPOL}{2005 -- Present}
    {Computer Science Engineering (in progress)}{Guayaquil, Ecuador}
  \resumeHeadingListEnd{}
%---------------------------------------------

\end{document}
